Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-10 WSSSPE1_report/WSSSPE1_summary_report.tex
small edits to new text

>>>>

It should be noted that several articles that discussed long-term projects, that
could be said to have reached a sustainable period. The Visualization Toolkit
(VTK) was described~\cite{Hanwell_WSSSPE} as being one of the oldest projects
serving as a basis for several other tools such as ParaView~\cite{Hanwell_WSSSPE}, VisIt~\cite{Ahern_WSSSPE}, and VisTrails~\cite{Koop_WSSSPE}. Other examples of
long-term, sustainable projects included MVAPICH~\cite{Panda_WSSSPE} and R/qtl~\cite{Broman_WSSSPE}, which both began development
in 2000, and DUNE~\cite{Blatt_WSSSPE}, which is also over a decade old. In
addition to how long a project has been active, other metrics are important,
such as number of developers, number of institutions, and whether there are
active developers acting as advocates for the continued viability of a project
beyond individual projects and/or institutions.
